### 2017-03-23 paper/topologySkeletons.tex
minor
first draft of the Future chapter

\section{Topology Skeletons}
Even though many algorithms can be expressed by parallel maps, some problems require more sophisticated skeletons. The Eden library leverages this problem and already comes with more predefined skeletons, among them the \code{pipe}, \code{ring} and a \code{torus} implementation \cite{eden_cefp, eden_skel_topology}. These seem like reasonable candidates to be ported to our arrow based parallel Haskell to prove that we can express such skeletons with Arrows as well.

>>>>

\section{Topology Skeletons}
Even though many algorithms can be expressed by parallel maps, some problems require more sophisticated skeletons. The Eden library leverages this problem and already comes with more predefined skeletons, among them are a \code{pipe}, \code{ring} and a \code{torus} implementation \cite{eden_cefp, eden_skel_topology}. These seem like reasonable candidates to be ported to our arrow based parallel Haskell to prove that we can express such skeletons with Arrows as well.
